Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

In relation to Bitcoin,researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p. 7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017). Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further. Based on analysis of the influence of twitter bullishness on the stock market by Mao et al. (2015), this paper further elaborates on the concept by applying the approach to Bitcoin prices.\\

\subsection{Data Collection}
For our data, we collected 2 separated time series datasets. One showing the twitter activity regarding bitcoin and the second one showing the bitcoin price development. Both datasets, were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC. We chose the hourly basis to be able to do a statistical analysis with a certain amount of observations in the restricted processing time for this homework. For the twitter data we aggregated every hour the total number of tweets mentioning bitcoin. For the bitcoin prices we selected prices at the last second of every hour.\\
The following figure displays the twitter activity regarding bitcoin for the observed time period. The first plot shows the hourly change of the aggregate number of tweets containing bitcoin. In the second and third plots we did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis. The graphs show overall a cyclical movement arount 1200 tweets and a single outburst on the 22.12.2017 for the time interval between 15:00:01 and 21:00:00 with highest value being 4622 tweets in one hour.\\

>>>>

In relation to Bitcoin,researchers already showed that analysing investors sentiments can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p. 7), by either using a \textit{polarity classification} – classifying the language in tweets as either positive or negative (see Colianni et al., 2015) – or a \textit{lexicon based approach} – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017). Hence, this paper choses a different focus area by limiting its scope to the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further. inspired on analysis of the influence of twitter bullishness on the stock market by Mao et al. (2015), this paper applies the similar method to Bitcoin prices.\\

\subsection{Data Collection}
For our data, we collected 2 separate time series datasets. One showing the twitter activity regarding bitcoin and the second one showing the bitcoin price development. Both datasets, were collected hourly for the period from the 19.12.2017 starting at 20:00:00 UTC and ending on the 28.12.2017 at 10:00:00 UTC. We chose the hourly basis to be able to do a statistical analysis with a certain amount of observations in the restricted processing time for this homework. For the twitter data we aggregated every hour the total number of tweets mentioning bitcoin. For the bitcoin prices we selected prices at the last second of every hour.\\
The following figure displays the twitter activity regarding bitcoin for the observed time period. The first plot shows the hourly change of the aggregate number of tweets containing bitcoin. In the second and third plots we did a first difference and a logarithmic first difference transformation of our main variable, in case it is needed in the later analysis. The graphs show overall a cyclical movement arount 1200 tweets and a single outburst on the 22.12.2017 for the time interval between 15:00:01 and 21:00:00 with highest value being 4622 tweets in one hour.\\
